Countering language attrition with PanLex and the Web of Data

### 2014-03-09 panlex-rdf-paper/2012/MLOD_PanLex/paper_v5.tex
proof read +  alternative fig 2

\section{Triplification of the Raw Data}
\label{sec:triplificate}
In this section, we analyze the PanLex dataset; introduce our URI and vocabulary design, which resemble PanLex's conceptual model;
%, which was developed independently from other ontology engineering approaches.
summarize how we classified PanLex's instance data with additional data models; and explain our transformation of the data to RDF.

>>>>

\section{Triplification of the Raw Data}
\label{sec:triplificate}
In this section, we analyze the PanLex dataset, introduce our URI and vocabulary design, which resemble PanLex's conceptual model,
%, which was developed independently from other ontology engineering approaches.
summarize how we classified PanLex's instance data with additional data models and explain our transformation of the data to RDF.
